---
title: "Selling Carseats and Linear Regression"
author: "Laura Cline"
date: "02/08/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(MASS)
library(ISLR)
```

```{r}
write.csv(Carseats, "carseats.csv")
```

# Qualitative Predictors 

We will attempt to predict `Sales` (child car seat sales) in 400 locations based on the number of predictors. 

```{r}
names(Carseats)
```

The `Carseats` data includes qualitative predictors such as `Shelveloc`, an indicator of the quality of the shelving location - that is, the space within a store that the car seat is displayed - at each location. The predictor `Shelveloc` takes on three possible values, *Bad*, *Medium*, and *Good*. Given a qualitative variable such as `Shelveloc`, R generates dummy variables automatically. Velow we fit a multiple linear regression model that includes some interaction terms. 

```{r}
lm.fit = lm(Sales ~.+ Income:Advertising + Price:Age, data = Carseats)
summary(lm.fit)
```

The `contrasts()` function returns the coding that R uses for dummy variables. 

```{r}
contrasts(Carseats$ShelveLoc)
```

Use '?contrasts` to learn about other contrasts and how to set them. 
R has created a `ShelveLocGood` dummy variable that takes on the value of 1 is the shelving location is good, and 0 otherwise. It has also created a `ShelveLocMedium` dummy variable that equals 1 if the shelving location is medium, and 0 otherwise. A bad shelving location corresponds to a zero for each of the two dummy variables. The fact that the coefficient for `ShelveLocGood` in the regression output is positive indicates that a good shelving location is associated with high sales (relative to a bad location). And `ShelveLocMedium` has a smaller positive coefficient, indicating that a medium shelving location leads to higher sales than a bad shelving location but lower sales than a good shelving location.

# Linear Regression 

```{r}
fit_1 = lm(Sales ~ Price + Urban + US, data=Carseats)
summary(fit_1)
```


```{r}
fit_2 = update(fit_1, . ~ . - Urban)
```

```{r}
confint(fit_2, level = 0.95)
```

